Inferring ecological interactions

### 2017-03-09 ms/ms_interactions.tex
Added some text in the fourth corner section

\subsubsection*{fourth-corner approaches}
\label{fourth-corner approaches}

A way to assess

An alternative approach is to use multivariate statistics to create association
matrices. One such method is called fourth-corner analysis, which is a type of
three table ordination (sometimes called `RLQ' analysis) (Doledec 1996). In
bipartite networks, fourth-corner analysis relates the matrix of species
interactions to a matrix of traits from one level (e.g.~plants) to another level
(e.g.~pollinators) via the matrix of species innteractions (Dray \& Legendre,
2008). This produces a correlation matrix, which is then compared to a null
expectation through matrix randomization. Randomization is a familiar tool in
network ecology, in which permuatation rules are used to compare the observed
test statistic (e.g the correlation among species occurrences) to a null
distribution based on some matrix constraint. Common constraints include the
mantainance of row sums, column sums, or other all marginal values, such that
only the identity of partners are switched. After each permutation, the test
statistic is recalulcating, yielding a null distribution. By comparing whether
the observed test statistic falls within the upper or lower 5th quantile of the
null distribution, studies distinguish whether their results could have been
generated at random given their sampling effort.

>>>>

\subsubsection*{fourth-corner modelling}
\label{fourth-corner modelling}

Fourth corner models originated from the work of \cite{doledec_matching_1996},
who proposed a way to perform an ordination called the `RLQ analysis', and
\cite{legendre_relating_1997}, who proposed a statistical  procedure to tests
the relationships among three data tables called the `fourth corner problem'.
Originally, the three data tables described a set of species found at different
locations, a set of environmental variables found at the same locations and a
set of species traits related associated to each species (\#\#\# Figure
conceptual 4th corner \#\#\#). Following these two seminal papers, a series of
developments have been proposed extending and generalizing and linking the `RLQ
analysis' and the `fourth corner problem' \cite{dray_testing_2008,
dray_combining_2014}.

In the context of ecological interactions, a different set of three matrices are
used. A matrix of species interactions is used as a basis which is related with
a matrix of traits for both side of the interacting species (\#\#\# Figure
conceptual 4th corner \#\#\#). These different developments are interesting to
evaluate and test the relationship among species, however they are not designed
to make predictions. To solve this issue, \cite{nygaard_new_2004},
\cite{pollock_role_2012}, \cite{jamil_selecting_2013},
\cite{brown_fourth-corner_2014} have independently proposed developments to make
predictions when dealing with three related matrices. In essence, these new
developments rely on hierarchical models \cite{gelman_data_2007}.

%%% ICI %%%
%%% ICI %%%
%%% ICI %%%
%%% ICI %%%
\section*{Literature cited}\label{literature-cited}
